Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-10 main.tex
temp - there are some missing references

\begin{document}

@@

    %%% MOTIVATION %%%
    Modern computing platforms are often heterogeneous, meaning they feature varying CPU speeds
    and memory sizes. In general, varying memory sizes make it more challenging to compute
    a schedule that respects all memory constraints -- meaning that no task is executed on a 
    processor with less memory than needed for the task. This is, however, very important to
    avoid (possibly expensive) runtime failures and to provide a satisfactory user experience.
    Hence, building on previous related work~\cite{TODO}, we consider a scheduling problem 
    formulation that takes memory sizes as explicit constraints into account. Its objective is
    the very common \emph{makespan}~\cite{liu2018survey}, 
    which acts as proxy for the total execution time of a workflow.

    A seminal list scheduling heuristic for workflows is HEFT 
    (heterogeneous earliest finish time)~\cite{topcuoglu2002performance}.
    It has two phases: (i) each task is assigned a priority and (ii) the tasks in a priority-ordered list are assigned
    to processors, where the ``ready'' task with the highest priority is scheduled next.
    HEFT has been extended (e.g.\ by Shi and Dongarra~\cite{SHI2006665}) and adjusted for a variety of different scheduling problem formulations. 
    Yet, none of them adheres to memory constraints -- also see our discussion of related work
    in Section~\ref{sec:related-work}. (\skug{check in related work if true!}).
        \skug{Note: 2 papers that deal with memory sizes, but model is very different!}

    Another limitation in practice of HEFT (and many other scheduling strategies) is their 
    assumption that the task running times provided to them are accurate. In practice this is 
    not the case and deviations from user estimates or historical measurements are 
    very common~\cite{TODO}. As a consequence, one should adapt the schedule when \emph{major}
    deviations occur. List-based schedulers such as HEFT are, however, not designed for 
    such an adaptation~\cite{TODO}.\hmey{Svetlana, Anne: is this a fair statement?}
%    and would compute a completely new schedule from scratch.

    %%% CONTRIBUTION %%%
    \paragraph*{Contribution} In this paper, we first propose three HEFT-based heuristics
    that adhere to memory size constraints: \heftbl, \heftblc, and \heftmm
    (M behind HEFT for \underline{m}emory, BL for \underline{b}ottom \underline{l}evel,
    BLC for \underline{b}ottom \underline{l}evel with \underline{c}ommunication, 
    and MM for \underline{m}inimum \underline{m}emory traversal).
    The difference between the new heuristics is the way they prioritize tasks (for processor assignment).
    We compare the static schedule produced by these heuristics with a HEFT variant as
    baseline that does not take memory sizes into account. \hmey{Need to clarify: 
    why is this SotA?}

@@

    \textit{Assignment to processor}
    When assigning the task, we set the ready time of the processor~$j$ $rt_j$ to the finish time of the task.
    For every predecessor of~$v$ that has been assigned to another processor, we adjust ready times on
    communication buffers $rt_{j', j}$ for every predecessor $u$'s processor $j'$: we increase them by the
    communication time $c( u,v) / \beta$.

@@

>>>>

\renewcommand{\iec}{i.e., }
\begin{document}

@@

    %%% MOTIVATION %%%
    Modern computing platforms are often heterogeneous, meaning they feature varying CPU speeds
    and memory sizes. In general, having different memory sizes per CPUs makes it more challenging to compute
    a schedule that respects all memory constraints -- meaning that no task is executed on a 
    processor with less memory than needed for the task. This is, however, very important to
    avoid (possibly expensive) runtime failures and to provide a satisfactory user experience.
    Hence, building on previous related work~\cite{TODO}, we consider a scheduling problem 
    formulation that takes memory sizes as explicit constraints into account. Its objective is
    the very common \emph{makespan}~\cite{liu2018survey}, 
    which acts as proxy for the total execution time of a workflow.

    A seminal list scheduling heuristic for workflows on heterogeneous platforms is HEFT 
    (heterogeneous earliest finish time)~\cite{topcuoglu2002performance}.
    It has two phases: (i) each task is assigned a priority; and (ii) the tasks in a priority-ordered list are assigned
    to processors, where the ``ready'' task with the highest priority is scheduled next on the processor
    where it would complete its execution first. 
    HEFT has been extended (e.g., by Shi and Dongarra~\cite{SHI2006665}) and adjusted 
    for a variety of different scheduling problem formulations. 
    Yet, none of them adhere to memory constraints as we propose -- see discussion of related work
    in Section~\ref{sec:related-work}. 
%    (\skug{check in related work if true!}).
%        \skug{Note: 2 papers that deal with memory sizes, but model is very different!}

    Another limitation in practice of HEFT (and many other scheduling strategies) is their 
    assumption that the task running times provided to them are accurate. In practice, this is 
    not the case and deviations from user estimates or historical measurements are 
    very common~\cite{TODO}. As a consequence, one should adapt the schedule when \emph{major}
    deviations occur. List-based schedulers such as HEFT are, however, not designed for 
    such an adaptation~\cite{TODO}.\hmey{Svetlana, Anne: is this a fair statement?}
%    and would compute a completely new schedule from scratch.

    %%% CONTRIBUTION %%%
    \paragraph*{Contribution} In this paper, we first propose three HEFT-based heuristics
    that adhere to memory size constraints: \heftbl, \heftblc, and \heftmm
    (M behind HEFT for \underline{m}emory, BL for \underline{b}ottom \underline{l}evel,
    BLC for \underline{b}ottom \underline{l}evel with \underline{c}ommunication, 
    and MM for \underline{m}inimum \underline{m}emory traversal).
    The difference between the new heuristics is the way they prioritize tasks (for processor assignment).
    We compare the static schedule produced by these heuristics with the classical HEFT as
    baseline, which however does not take memory sizes into account. 
    \hmey{Need to clarify: why is this SotA?}

@@

    \textit{Assignment to processor. }
    When assigning the task, we set the ready time $rt_j$ of  processor~$j$ to be the finish time of the task.
    For every predecessor of~$v$ that has been assigned to another processor, we adjust ready times on
    communication buffers $rt_{j', j}$ for every predecessor $u$'s processor $j'$: we increase them by the
    communication time $c( u,v) / \beta$.

@@

Extend to heterogeneous bandwidths.
